Black and White Life Expectancy Differences in 4 US States, 1969-2013

### 2019-07-18 Manuscript2/ageCOD_manuscript.Rmd

age_cod_results <- age_cod_results %>% group_by(state, year, sex, COD, age_collapse) %>%
  mutate(age_COD_cont_yrs_mean_collapse = sum(age_COD_cont_yrs_mean))
```

>>>>

age_cod_results <- age_cod_results %>% group_by(state, year, sex, COD, age_collapse) %>%
  mutate(age_COD_cont_yrs_mean_collapse = sum(age_COD_cont_yrs_mean))

men_cod_contributions <- age_cod_results %>% ungroup() %>% filter(sex == "Male", state %in% c("California", "New York", "Illinois", "Georgia"))

women_cod_contributions <- age_cod_results %>% ungroup() %>% filter(sex == "Female", state %in% c("California", "New York", "Illinois", "Georgia"))
```
